---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, here-i-am-emma}
here::i_am(
  "subproject_emma/report.Rmd"
)
```

# Logistic Regression Analysis

## Regression Model

To assess whether age increases the risk of intubation, we fit a logistic regression model with intubation as the response variable and age as the explanatory variable.

```{r, model}
intubation_age_results <- readRDS(
  file = here::here("subproject_emma/output/intubation_age_results.rds")
)
```

The fitted logistic regression model was
$$
\log\left(\frac{p}{1-p}\right) = -2.2862 + 0.0136(\text{Age}),
$$
where \(p\) represents the probability of intubation. The estimated slope for age is positive, indicating that older age is associated with higher odds of intubation.

## Regression Table

Below is the regression table for the logistic regression model.

```{r, table}
intubation_age_results$table
```

## Graphical Analysis

Below is a bar chart showing the intubation rate by age group.

```{r}
knitr::include_graphics(
  here::here("subproject_emma/output/intubation_rate_by_age_group.png")
)
```

